---
title: "Coral Cover (2D Training)"
author: "Jon Peppinck"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
fig_width: 7
fig_height: 3
vignette: >
  %\VignetteIndexEntry{Coral Cover (2D Training)}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
  
```{r setup, include = FALSE}
  knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.height = 3,
  fig.width = 7
  )
require(knitr)
```
  
# Annotate 2D Virtual Reality Images by Creating an Interactive WebVR scene

`r2vr` has been extended to be able to help train users to annotate virtual reality images more accurately. The 2D Training will randomly select `3` images from a pool of images. Users are able to annotate selected markers (for each image) as either `C` or `N` to classify the bounded region as either containing mostly `Coral` or `Not Coral` respectively. The user's annotations are then compared to a `gold standard`, which are the correct annotations for the corresponding fixed points in which the user annotated. The user will then be able to receive visual feedback with markers changing to `green` or `red` depending on if they annotated the marker correctly or incorrectly respectively.

## Case Study: Coral Cover

TODO

```{r}
library(r2vr)

## Find the IPv4 Address
```
